---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "85%",
  dev = 'png'
)
```

# {huckster}

<!-- badges: start -->
[![R-CMD-check](https://github.com/brownag/huckster/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/brownag/huckster/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of {huckster} is to provide tools for easily obtaining boundaries of hydrologic units and other information based on Hydrologic Unit Codes ('HUC'). 

Hydrologic unit data are retrieved from the U.S. Geological Survey 'NationalMap' REST API by default. This endpoint can be customized: \<https://hydro.nationalmap.gov/arcgis/rest/services/wbd/MapServer/>.

## Installation

You can install the development version of {huckster} from [GitHub](https://github.com/brownag/huckster) with:

``` r
# install.packages("remotes")
remotes::install_github("brownag/huckster")
```

## Examples

Here are some basic examples showing how to obtain hydrologic unit boundaries by ID (code), point, envelope, and polygon. 

The default `layerid=5` corresponds to a "10-digit" HUC or "watershed" level boundary. See `huc_code()` for a system for encoding `layerid` from labels, code lengths or codes.

```{r examples}
library(huckster)
library(terra)

## HUC code input
ids <- c("071000050101",  "071000050102",
         "071000050103",  "071000050104")
w <- id_to_huc(ids, layer = "subwatershed")

plot(w)

## point input
x <- point_to_huc(-94.0671, 43.026, layer = "subbasin")

plot(x)

## SpatExtent bounding box/envelope input
y <- envelope_to_huc(terra::ext(x))

## equivalently using numeric bounds:
# y <- envelope_to_huc(-94.150, 42.298, -93.636, 43.156)

plot(y)

## SpatVector polygon ('Ditch Number 71' rect extent) as input
p <- terra::as.polygons(y[1, ], ext = TRUE)
z <- polygon_to_huc(p, layer = "subwatershed")

plot(z)
plot(p, col = rgb(1, 0, 0, 0.5), add = TRUE)
```
