---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "85%",
  dev = 'png'
)
```

# {huckster}

<!-- badges: start -->
[![R-CMD-check](https://github.com/brownag/huckster/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/brownag/huckster/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of {huckster} is to provide tools for easily obtaining boundaries of hydrologic units and information based on Hydrologic Unit Codes ('HUC'). Hydrologic unit data are retrieved from the USGS NationalMap ArcGIS MapServer web services: <"https://hydro.nationalmap.gov/arcgis/rest/services/wbd/MapServer/>.

## Installation

You can install the development version of {huckster} from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("brownag/huckster")
```

## Example

Here are some basic examples showing how to obtain hydrologic unit boundaries by ID, point, envelope, and polygon. The default `layerid` is `5` which corresponds to a "10-digit" HUC.

```{r examples}
library(huckster)
library(terra)

ids <- c("071000050101",  "071000050102",  "071000050103",  "071000050104")
w <- id_to_huc(ids, layerid = 6)
plot(w)

x <- point_to_huc(-94.0671, 43.026, layerid = 4)
plot(x)

# bounding box/envelope numeric input
y <- envelope_to_huc(terra::ext(x))
plot(y)

# SpatVector polygon (Prairie Creek rect extent) as input
p <- as.polygons(y[1, ], ext = TRUE)
z <- polygon_to_huc(p, layerid = 6)
plot(z)
plot(p, col = rgb(1, 0, 0, 0.5), add = TRUE)
```
